Increasing Performance via Gamification in a Volunteer-Based Evolutionary Computation System

### 2018-01-06 2018-IPMU/Gamification/paper.tex
Revises conclusions closes #7

In this paper we have added gamification to a volunteer computing
system via a leaderboard of contributions of registered users. The objective of this work was to test the kind of impact
applying a gamification technique has on user engagement in
the Anonymous
% {\sf NodIO}
volunteer computing framework; in concordance with
the results obtained in other
browser-based volunteer systems, after
applying the gamification techniques, registered users participated much more intensely than anonymous ones.

@@

Other factors, such as the language used, the way the experiment is announced, are also very important in this social context, which is why they will be included in future lines of work too.

One of the interesting future lines of work would be to look a bit
more closely at the behavior of users as they are participating
in the web system.

@@

% This work has been supported in part by: Ministerio espa\~{n}ol de
% Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-3-P
% (UGR-EPHEMECH).
Hidden for double blind.

>>>>

In this paper we have added gamification to a volunteer computing
system via a leaderboard of contributions of registered users. The objective of this work was to test the kind of impact
applying a gamification technique has on user engagement in
the {\sf NodIO}
volunteer computing framework; in concordance with
the results obtained in other
browser-based volunteer systems, after
applying the gamification techniques, registered users participated much more intensely than anonymous ones.

@@

Other factors, such as the language used, the way the experiment is
announced, are also very important in this social context, which is
why they will be included in future lines of work too, along with the
study of the behavior of users as they are participating
in the web system.

@@

This work has been supported in part by: Ministerio espa\~{n}ol de
 Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-3-P
 (UGR-EPHEMECH).
